Methods for Large Scale Learning to Rank

### 2014-04-06 report/Chapters/CrossBenchmarkComparison.tex
begin werk aan 'proposed by'-references

AdaRank-\acs{MAP} &  &  & Linear Regression &  & \cite{Wang2012, Volkovs2011} \\ 
AdaRank-\acs{nDCG} &  & \cite{Busa-Fekete2013,Tan2013} & List\acs{MLE} &  & \cite{Lin2010, Lin2011, Gao2014} \\ 

@@

BagBoo &  & \cite{Ganjisaffar2011c} & MCP & \cite{Laporte2013} & \cite{Laporte2013} \\ 

@@

CA &  & \cite{Busa-Fekete2013,Tan2013} & Q.D.\acs{KNN} &  & \cite{Wang2013} \\ 
CCRank &  &  & RandomForest &  & \cite{Gomes2013} \\ 

>>>>

AdaRank-\acs{MAP} & \cite{Xu2007} &  & Linear Regression &  & \cite{Wang2012, Volkovs2011} \\ 
AdaRank-\acs{nDCG} & \cite{Xu2007} & \cite{Busa-Fekete2013,Tan2013} & List\acs{MLE} &  & \cite{Lin2010, Lin2011, Gao2014} \\ 

@@

BagBoo & \cite{Pavlov2010} & \cite{Ganjisaffar2011c} & MCP & \cite{Laporte2013} & \cite{Laporte2013} \\ 

@@

CA & \cite{Metzler2007} & \cite{Busa-Fekete2013,Tan2013} & Q.D.\acs{KNN} &  & \cite{Wang2013} \\ 
CCRank & \cite{Wang2011c} & \cite{Wang2011c} & RandomForest &  & \cite{Gomes2013} \\ 
